A framework for mentored data science research

### 2019-12-08 Rmd/methods.Rmd
added markdown table
added backward design fig1

>>>>

```{r t1, echo = FALSE}
library(magrittr)
step <- c(rep("Question formulation", 3),
          rep("Data acquisition", 3), 
          rep("Data analysis and visualization", 2), 
          rep("Presentation and communication", 3)
)
details <- c("List ideas", "Prioritize ideas", "Check data availability",
             "Download tweets and other data", "Parse tweet JSON", "Organize data as times series",
             "Exploratory plots", "Summary statistics",
             "Interpret and summarize graphs and summary statistics", "Prepare written materials and figures", "Share findings as posters, slides, and reports"
             )
tibble::tibble(step, details) %>%
#  dplyr::group_by(step) %>%
  gt::gt() %>%
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "lightcyan"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Question formulation"
      )
  ) %>%
    gt::tab_style(
    style = list(
      gt::cell_fill(color = "pink"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Data acquisition"
      )
  ) %>%
  gt::tab_header(
    title = gt::md("Framework Overview"), subtitle = "xxx"
  ) %>%
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "apricot"),
      gt::cell_text(style = "italic")
      ),
    locations = gt::cells_data(
      columns = dplyr::vars(details),
      rows = step == "Data analysis and visualization"
      )
  )
```
